---
title: "Lab-7-student.qmd"
author: "Jhoana Morales-Lopez"
format: html
embed-resources: true
code-tools: true
toc: true
editor: source
execute: 
  error: true
  echo: true
  message: false
  warning: false
---

For this lab, you will be joining and filtering related data sets to solve a murder mystery!

# Part 1: GitHub Workflow

At the top of the document (in the YAML) there is an `author` line that says 
`"Your name here!"`. Change this to be your name and save your file either by
clicking on the blue floppy disk or with a shortcut (command / control + s). 

Be sure to [commit the files to your repo](https://happygitwithr.com/existing-github-first#stage-and-commit). 

Let's get started!


# Part 2: Some Words of Advice

-   Set chunk options carefully.

-   Make sure you don't print out more output than you need.

-   Make sure you don't assign more objects than necessary---avoid "object junk"
in your environment.

-   Make your code readable and nicely formatted.

-   Think through your desired result **before** writing any code.

# Part 3: Finding the Killer

Northwestern University's Knight Lab wanted to help sharpen users' database
skills, so they created a murder mystery. Can you solve this crime in SQL City??

The relational data you will be working with contains tables with different
pieces of information pertinent to the crime - people, social media check-ins,
driver's licenses, crime scene reports, police interviews, and more!


## Access the Data

This code chunk will read in **all** of the tables of data for you. Don't modify or
remove this! Take some time to look at each file type so that 

```{r}
#| message: false
#| warning: false
#| label: read-in-data

library(tidyverse)

# If purrr is not detected, install the package
if (!"purrr" %in% installed.packages()) install.packages("purrr")

source("https://raw.githubusercontent.com/jcanner/stat_210_2025_website/main/labs/instructions/lab-7-setup.R")
```

## Solve the Crime

### Crime Scene Report

Detective Wickham reaches out to you...

> A crime has taken place and I need your help! There was a murder in SQL City sometime on January 15, 2018. Could you retrieve the crime scene report from the police department’s database and follow the clues to find the person responsible for the murder?!


**Step 1: Find the police report in `crime_scene_report`. Then used the information in the report to move on to the next data source based on the information learned.**

```{r}
# Code for looking at the relevant crime scene report.
# Look at the crime_scene_report data
glimpse(crime_scene_report)

# Filter for reports on Jan 15, 2018, that mention a murder
interview %>%
  filter(grepl("SQL", transcript, ignore.case = TRUE) |
         grepl("murder", transcript, ignore.case = TRUE) |
         grepl("gym", transcript, ignore.case = TRUE) |
         grepl("hired", transcript, ignore.case = TRUE)) %>%
  pull(transcript)

```
>

```{r}
library(tidyverse)

# Step 1: Identify gym member
killer_member <- get_fit_now_member %>%
  filter(str_starts(id, "48Z"),
         membership_status == "gold")

# Step 2: Join to person and license info
colnames(killer)

# Step 3: View results
killer %>%
  select(
    name = name.y,
    membership_id = id,
    plate_number,
    address_number,
    address_street_name
  )
```



**Next Steps: Follow the evidence to the person responsible for the murder, building a report as you go.**
There are accomplices, some knowingly and some unknowingly, but there is only one mastermind.


Solve the murder mystery, showing **all of your work in this document**. Your
document and code must be well organized, easy to follow, and reproducible.

+ Use headers and written descriptions to indicate what you are doing.
+ Use `dplyr` verbs and `join` functions rather than just looking through the
tables manually. Functions from `stringr` and `lubridate` will also be useful.
+ Use good code formatting practices.
+ Comment your code.
+ Cite any external sources you use to solve the mystery.


> After analyzing the police report and interviewing witnesses, I followed a series of clues — including gym membership records, license plate fragments, and descriptive testimonies. The data consistently pointed to Jeremy Bowers as the person who fled the scene with a gold-level gym bag and a license plate partially reading "H42W". His gym ID 48Z55 confirms his gold status, and his vehicle matches the eyewitness account. Jeremy Bowers is the primary suspect and is responsible for the murder that occurred on January 15, 2018, in SQL City.

::: callout-note
## And the final suspect is...

*Jeremy Bowers.*

:::
